A Data-Driven Framework for Neural Field Modelling

### 2010-10-29 ltx/first_order_framework/LaTeX_Manuscript.tex
Changed Figure5

\begin{figure*}[!ht] 
\begin{center}
\includegraphics{./Graph/pdf/Figure5.pdf}	
\end{center}
\caption{{\bf Spatial frequency analysis}. The dashed line shows the cut-off frequency (-3 dB point). (\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations. (\textbf{B}) The spatial frequency response of a one-dimensional model sensor. The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics. (\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors. }
\label{fig:Figure5}
\end{figure*}

>>>>

\begin{figure*}[!ht] 
\begin{center}
\includegraphics{./Graph/pdf/Figure5.pdf}	
\end{center}
\caption{{\bf Spatial frequency analysis}. The dashed line shows the cut-off frequency (-3 dB point). (\textbf{a}) The average (over time) power in dB of the spatial frequency of the observations. (\textbf{b}) The spatial frequency response of a one-dimensional model sensor. The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics. (\textbf{c}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors. }
\label{fig:Figure5}
\end{figure*}
